\documentclass[12pt,letterpaper,unicode]{moderncv}

\moderncvtheme{classic}
\usepackage[utf8]{inputenc}


\usepackage[scale=.85]{geometry}          % smaller number -> text takes more space
\AtBeginDocument{\recomputelengths}

% Hyperlinks
\usepackage[unicode]{hyperref}                      % to use hyperlinks
\definecolor{linkcolour}{rgb}{0,0.2,0.6}            % hyperlinks setup
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Frederick}
\familyname{Robinson}
\address{}{San Francisco, CA}
\phone{(321) 613-8838}
\email{frederick.robinson@gmail.com}


\nopagenumbers{}                    

\begin{document}
\vspace*{-7mm}
\hypersetup{pdftitle={Frederick Robinson}} %% sets title in PDF Metadata
\maketitle
\vspace*{-7mm}

\section{Employment}


\cventry{2024--2025}{Principal Applied Scientist (later Member of Technical Staff)}{Amazon SF AI Lab}{San Francisco, CA}{}{
\begin{itemize}
    \item{Early member of Amazon’s SF AI Lab, reestablishing infra and experimentation pipelines after Adept’s transition.}
    \item{Founding member of the reinforcement learning group, setting up RLHF systems and advancing CoT/RLVR training.}
    \item{Drove technical leadership through open-source contributions, mentoring, and engineering best practices.}
\end{itemize}
}

\cventry{2024}{Member of Technical Staff}{Adept}{San Francisco, CA}{}{
\begin{itemize}
    \item{Improved reliability of computer-use agents by developing evaluation frameworks, data collection pipelines, and SFT experiments.}
    \item{Worked across modeling, infra, and evaluation in a fast-paced startup environment.}
    \item{Contributed foundational work that supported the team’s transition into Amazon.}
\end{itemize}
}

\cventry{2022-2023}{Staff Machine Learning Engineer}{Stripe, Inc.}{Supportability Intelligence}{}{
\begin{itemize}
    \item{Led a cross-functional team of ML and backend engineers, delivering $>20\%$ improvement in Terms of Service violation enforcement with LLMs.}
    \item{Developed a transformer-based merchant website text classification model and a new service centralizing merchant business model data.}
    \item{Scoped and delivered ML-driven systems that improved Stripe’s risk intelligence and supportability.}
\end{itemize}
}
\cventry{2017-2022}{Senior Applied Scientist}{Amazon AWS - Interactive Video Service}{Twitch}{}{
\begin{itemize}
    \item{Designed and productionized ML models to optimize data center selection for video playback, reducing global buffering rates by  $>1\%$.}
    \item{Created streaming fraud detection system, improving detection of viewbot activity by  $>75\%$.}
    \item{Launched ML service predicting optimal video player settings and provided technical mentorship to applied scientists on research and engineering best practices.}
\end{itemize}
}
\cventry{2014--2017}{Software Engineer}{Google, Inc. -- Display Ads}{Remarketing Quality}{}{
\begin{itemize}
    \item{Built ML models and real-time bidding systems that optimized advertiser ROI and unlocked tens of millions in incremental annual revenue.}
\end{itemize}
}

\section{Skills}
\cvline{Skills}{Large Language Models, Reinforcement Learning (RLHF, CoT, RLVR), Supervised Fine-Tuning, Evaluation Frameworks, Distributed Training Systems, Data Collection Pipelines, Python, Golang}


\section{Education}
\cventry{2014}{Master of Arts in Mathematics}{University of California Los Angeles}{}{}{}
\cventry{2012}{Bachelor of Arts in Mathematics with Honors}{Northwestern University}{}{}{}

\end{document}
